Figure 4 - Motifs

### 2024-07-15 ms_figure_4_motifs.Rmd
rename Fig3 to Fig4

---
title: "Figure 3 - Motifs"
author: "Michael Stadler, Charlotte Soneson, Merle Skribbe"
date: "`r Sys.Date()`"
output: 
    html_document:
        theme: united
        toc: true
        toc_float: true
        code_folding: hide
params:
    dbdtxt: "data/TF_DBD_annotation.txt"
    motifrds: "data/motifs_annotated.rds"
    peakcsv: "data/fused_peaks_filtered.csv.gz"
    genomefasta: "reference/Schizosaccharomyces_pombe.ASM294v2.dna.toplevel.fa"
    ncpu: 4
editor_options: 
    chunk_output_type: console
---

@@

# Figure 3

@@

Assemble the panels into Figure 3:

```{r Fig3}
#| fig.width: 11
#| fig.height: 14

@@

Assemble the panels into Supplementary Figure 3:

```{r suppFig3}
#| fig.width: 4.5
#| fig.height: 6

>>>>

---
title: "Figure 4 - Motifs"
author: "Michael Stadler, Charlotte Soneson, Merle Skribbe"
date: "`r Sys.Date()`"
output: 
    html_document:
        theme: united
        toc: true
        toc_float: true
        code_folding: hide
params:
    dbdtxt: "data/TF_DBD_annotation.txt"
    motifrds: "data/motifs_annotated.rds"
    peakcsv: "data/fused_peaks_filtered.csv.gz"
    genomefasta: "reference/Schizosaccharomyces_pombe.ASM294v2.dna.toplevel.fa"
    ncpu: 4
editor_options: 
    chunk_output_type: console
---

@@

# Figure 4

@@

Assemble the panels into Figure 4:

```{r Fig4}
#| fig.width: 11
#| fig.height: 14

@@

Assemble the panels into Supplementary Figure 4:

```{r suppFig4}
#| fig.width: 4.5
#| fig.height: 6
